Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-07-25 paper/paper.methods.tex
Minor fix + update pdf

\subsection{Objectives}
As described in Section \ref{???}, the soft constraints of the clinician scheduling problem include: (1) satisfying clinician block off requests, (2) satisfying clinician weekend off requests, and (3) assigning weekends closer to blocks. We convert these soft constraints into linear objective functions of the binary variables defined in Section \ref{???}. The first two objectives can be written as the following linear functions:  %minor suggestion - consider numbering the objectives for ease later when saying things like "these two objectives"...or writing the full name of the objectives instead of 'this' and 'these' as sometimes can get confusing what the 'this' and the 'these' refer to. 
\begin{align}
	&Q_1(X) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{d=1}^{D} (-1)^{\ind(b\,\in\,\mathcal{BR}_c)}\cdot X_{c, b, d} \tag{Block Requests} \label{eqn:obj-block-requests}\\
	&Q_2(Y) = \sum_{c=1}^{C} \sum_{w=1}^{W} (-1)^{\ind(w\,\in\,\mathcal{WR}_c)}\cdot Y_{c, w} \tag{Weekend Requests} \label{eqn:obj-weekend-requests}
\end{align}
where $\ind(\cdot)$ is the indicator function that has value 1 when the condition is met and 0 otherwise. In the above two objectives, we penalize any assignments that conflict with a block or weekend request, and aim to maximize the non-conflicting assignments. The Block-Weekend Adjacency is optimized by considering the product $X_{c, b, d}\cdot Y_{c, w}$ for values of $w$ ``adjacent'' to the value of $b$. For instance, clinicians might want to be assigned during a weekend that falls within an assigned block. So if clinician $c$ is assigned to work during block 3, corresponding to weeks 5 and 6 assuming 2-week blocks, they might also want to be assigned to work during weekend 5. In that case, we would like $X_{c, b=3, d} \cdot Y_{c, w=5}$ to be 1, since that indicates both variables are assigned. If at least one of the two variables is not assigned, the product will be 0. This leads to the maximization objective  %avoid editorial adjectives
\begin{align}
	&Q_3(X, Y) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{d=1}^{D} X_{c, b, d}\cdot Y_{c, w=\varphi(b)} \tag{Block-Weekend Adjacency} \label{eqn:obj-block-weekend-adj}
\end{align}
where $\varphi(b)$ maps a block one-to-one to an adjacent weekend, by some appropriate definition of adjacency. For instance, in the above example we will have $\varphi(b) = 2b - 1$. \\
% I really liked the example explanation!

>>>>

\subsection{Objectives}
As described in Section \ref{???}, the soft constraints of the clinician scheduling problem include: (1) satisfying clinician block off requests, (2) satisfying clinician weekend off requests, and (3) assigning weekends closer to blocks. We convert these soft constraints into linear objective functions of the binary variables defined in Section \ref{???}. Objectives (1) and (2) can be written as the following linear functions:  %minor suggestion - consider numbering the objectives for ease later when saying things like "these two objectives"...or writing the full name of the objectives instead of 'this' and 'these' as sometimes can get confusing what the 'this' and the 'these' refer to. 
\begin{align}
	&Q_1(X) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{d=1}^{D} (-1)^{\ind(b\,\in\,\mathcal{BR}_c)}\cdot X_{c, b, d} \tag{Block Requests} \label{eqn:obj-block-requests}\\
	&Q_2(Y) = \sum_{c=1}^{C} \sum_{w=1}^{W} (-1)^{\ind(w\,\in\,\mathcal{WR}_c)}\cdot Y_{c, w} \tag{Weekend Requests} \label{eqn:obj-weekend-requests}
\end{align}
where $\ind(\cdot)$ is the indicator function that has value 1 when the condition is met and 0 otherwise. In the above two objectives, we penalize any assignments that conflict with a block or weekend request, and aim to maximize the non-conflicting assignments. The Block-Weekend Adjacency is optimized by considering the product $X_{c, b, d}\cdot Y_{c, w}$ for values of $w$ ``adjacent'' to the value of $b$. For instance, clinicians might want to be assigned during a weekend that falls within an assigned block. So if clinician $c$ is assigned to work during block 3, corresponding to weeks 5 and 6 assuming 2-week blocks, they might also want to be assigned to work during weekend 5. In that case, we would like $X_{c, b=3, d} \cdot Y_{c, w=5}$ to be 1, since that indicates both variables are assigned. If at least one of the two variables is not assigned, the product will be 0. This leads to the maximization objective  %avoid editorial adjectives
\begin{align}
	&Q_3(X, Y) = \sum_{c=1}^{C} \sum_{b=1}^{B} \sum_{d=1}^{D} X_{c, b, d}\cdot Y_{c, w=\varphi(b)} \tag{Block-Weekend Adjacency} \label{eqn:obj-block-weekend-adj}
\end{align}
where $\varphi(b)$ maps a block one-to-one to an adjacent weekend, by some appropriate definition of adjacency. For instance, in the above example we will have $\varphi(b) = 2b - 1$. \\
% I really liked the example explanation!
